\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
Abstract with Dominik's suggestions

  \begin{abstract}
   We introduce \fs, a \mathematica package which generates a fast,
   precise C++ spectrum generator for any SUSY model specified by the
   user.  The generated code is designed with both speed and
   modularity in mind, making it easy to adapt and extend with new
   features. The user specifies the model supplying the
   superpotential, gauge structure and particle content in a \sarah
   model file and provides the specific boundary conditions in a
   separate \fs model file. \fs makes use of the existing \sarah
   package to obtain self energies, tadpole corrections,
   renormalization group equations (RGEs) and tree level mass and
   electroweak symmetry breaking conditions for the specified model. These are
   translated into C++ code and combined  with numerical
   routines for solving the RGEs, EWSB conditions and simultaneously
   solving for the spectrum consistent with user specified boundary
   conditions.  The modular structure of the generated code allows for
   individual components to be replaced with an alternative if
   available. \fs has been carefully designed to grow as
   alternative solvers and calculators are added.
  \end{abstract}

>>>>

  \begin{abstract}
    We introduce \fs, a \mathematica package, which generates a fast,
    precise C++ spectrum generator for any SUSY model specified by the
    user.  The generated code is designed with both speed and
    modularity in mind, making it easy to adapt and extend with new
    features. The model is specified by supplying the superpotential,
    gauge structure and particle content in a \sarah model file;
    specific boundary conditions e.g.\ at the GUT, weak or
    intermediate scales are defined in a separate \fs model file.
    From these model files, \fs generates C++ code for self-energies,
    tadpole corrections, renormalization group equations (RGEs) and
    electroweak symmetry breaking (EWSB) conditions and combines them
    with numerical routines for solving the RGEs and EWSB conditions
    simultaneously.  The resulting spectrum generator is then able to
    solve for the spectrum of the model, including loop-corrected pole
    masses, consistent with user specified boundary conditions.  The
    modular structure of the generated code allows for individual
    components to be replaced with an alternative if available. \fs
    has been carefully designed to grow as alternative solvers and
    calculators are added.  Predefined models include the MSSM, NMSSM,
    \ESSM, USSM, $R$-symmetric models and models with right-handed
    neutrinos.
  \end{abstract}
